Breast cancer

### 2025-03-12 reporting/breast_cancer/breast_description.Rmd
adapt old scripts

lsdata <- readRDS(file = here::here("data/breast_cancer/datamanaged.rds"))

@@

ls_pathways <- lsdata$pathways
df_data <- lsdata$data

@@

```{r ecdf, fig.cap="Empirical Cumulative Distribution Function of number of genes by pathway. Breast cancer study."}
lapply(ls_pathways,
       function(pathway_i) sum(pathway_i %in% colnames(df_data))) |> 
  bind_rows() |> 
  tidyr::pivot_longer(cols = everything(),
                      names_to = "pathway",
                      values_to = "nb_genes") |> 
  ggplot(mapping = aes(x = nb_genes)) +
  stat_ecdf() +
  geom_point(y = 0, shape = "|") +
  theme_minimal() +
  labs(x = "Number of genes",
       y = "Empirical Cumulative Distribution")

>>>>

lsdata <- readRDS(file = here::here("data/breast_cancer/datamanaged2.rds"))

@@

df_pathways <- lsdata$pathways
df_data <- lsdata$data

@@

```{r ecdf, fig.cap="Empirical Cumulative Distribution Function of number of genes by pathway. Breast cancer study."}
df_pathways |> 
  group_by(gene_symbol) |> 
  summarise(nb_genes = n()) |> 
  ggplot(mapping = aes(x = nb_genes)) +
  stat_ecdf() +
  geom_point(y = 0, shape = "|") +
  theme_minimal() +
  labs(x = "Number of genes",
       y = "Empirical Cumulative Distribution")
```
